---
title: "Periodontitis with Gastro-Esophageal Reflux Disease (GERD)"
author: "Rhea"
date: "2023-08-07"
output: html_document
---

The Causal association between Periodontitis and GERD.
Gastro-Esophageal Reflux Disease (Exposure) -> Periodontitis (Outcome)

```{r}
library(TwoSampleMR)
## instrumental variable extracted from Exposure data
gerd = extract_instruments(outcomes = "ebi-a-GCST90000514",  p1 = 5e-08, clump = TRUE, p2 = 5e-06, r2 = 0.001, kb = 10000)
```
Outcome data (Periodontitis- European)
```{r}
gerdout.Perio = extract_outcome_data(snps = gerd$SNP, outcomes = "finn-b-K11_PERIODON_CHRON", proxies = FALSE, maf_threshold = 0.01)
```
Data Harmonization
```{r}
gerdmrdata.Perio = harmonise_data(exposure_dat = gerd, outcome_dat = gerdout.Perio, action = 2)
```
MR Analysis (with five models, alpha significance : 0.05)
```{r}
mr(gerdmrdata.Perio, method_list = c("mr_egger_regression", "mr_ivw", "mr_ivw_radial", "mr_ivw_mre", "mr_weighted_median"))
```
Causal Effects Tests (in-depth analysis)
Heterogeneity_Test
```{r}
b.1test = mr_heterogeneity(gerdmrdata.Perio)

mr_heterogeneity(gerdmrdata.Perio)
```
Pleiotropy_Test 
```{r}
b.2test = mr_pleiotropy_test(gerdmrdata.Perio)

mr_pleiotropy_test(gerdmrdata.Perio)
```
Leave-one-out Sensitivity Test
```{r}
b.3test = mr_leaveoneout(gerdmrdata.Perio)

mr_leaveoneout_plot(b.3test)
```
MR Scatter plot
```{r}
sp1 = mr(gerdmrdata.Perio)

mr_scatter_plot(sp1, gerdmrdata.Perio)
```
MR Forest plot
```{r}
mr_forest_plot(mr_singlesnp(gerdmrdata.Perio))
```
Funnel plot
```{r}
mr_funnel_plot(mr_singlesnp(gerdmrdata.Perio))
```
